Model-based variable selection for regression with highly correlated variables.

### 2014-05-06 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@571 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{document}
\begin{center}
{\Large
	{\sc Model-based variable selection for regression \\ with highly correlated variables.}
}
\bigskip

@@

{\bf Abstract.} Linear regression outcomes are known to be damaged by highly correlated covariates. However many modern datasets are expected to convey more and more highly correlated covariates due to the global increase of the amount of variables in datasets. We propose to explicitly model the correlations by a family of linear regressions between the covariates, some covariates explaining others. It allows then to obtain by marginalisation on the explained covariates a parsimonious correlation-free regression model, easily understandable. 
It corresponds to a kind of variable selection preliminary step which has then to be followed by standard linear estimation methods including classical variables selection procedures for instance. The structure of correlations is found with an MCMC algorithm aiming at optimizing a specific BIC criterion.
 An R package (\textsc{CorReg}) available on the CRAN implements this new method which will be illustrated on both simulated datasets and real-life datasets from steel industry where correlated variables are frequent.
\smallskip

@@

	With the rise of informatics, datasets contain more and more covariates, % and thus dimension reduction becomes a necessity. Moreover, 
	increasing the chance to have correlated ones.  
	 In such a context, variance of the estimators can lead to arbitrary results whereas interpretation and prediction are both strongly needed, depending on the context. For instance, interpretation could be favoured to improve a situation instead of only predict problems, so robust estimation is a real stake.
		~\\	~\\

%bibliographie	
	The Ordinary Least Squares (\textsc{OLS}) estimator is the minimum-variance linear unbiased estimator but it suffers from ill-conditioned matrices inversion when the covariates are highly correlated (section \ref{sectionOLS}). Therefore, some other methods try to improve the robustess of the estimator by introducing some bias, selecting only some covariates, grouping some covariates, {\it etc.}.

@@

	 Penalized methods try to reduce the variance introducing some bias to improve the bias-variance tradeoff and get better prediction.
	Ridge regression \cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty.
	But this penalty is not guided by the correlations. It is the same for each covariate and will be too large for independent covariates and/or too small for correlated ones. So the efficiency of such a method is limited. 
	Moreover, coefficients tend to 0 but don't reach 0 so it gives difficult interpretations for large number of covariates. The absence of variable selection is not compatible with the need to find small set of relevant covariates to explain the response variable.

@@

	But it requires to suppose having many covariates with the same level of effect on the response variable and seems to stay less efficient in prediction than elastic net.
	 Spike and Slab variable selection \cite{ishwaran2005spike} also relies on Gaussian mixture (the spike and the slab) hypothesis for the regression coefficients and gives a subset of covariates (not grouped) on which to compute \textsc{OLS} but has no specific protection against correlations issues.
	We see that none of the above methods takes explicitly the correlations into account, even if the clustering methods introduce a kind of relationship between the covariates.

	~\\	~\\
% Principe de la méthode

 Instead of reducing the dimension without looking at correlations, Selvarclust \cite{maugis2009variable} proposes to focus on the correlations, giving an explicit structure between covariates by linear sub-regressions between them. But it is made in a clustering context, with only irrelevant covariates being dependent from relevant ones (no sub-regressions between relevant or between irrelevant covariates) and the algorithm used to find the structure is a stepwise-like algorithm without protection against correlations \cite{raftery2006variable} even it is known to be often unstable \cite{miller2002subset}. We propose to develop this method for linear regression with a specifically adapted algorithm to find the structure of sub-regression.

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&$P(S)$ &indicator &OLS  &    \textsc{CorReg} $\hat S$ + OLS& \textsc{CorReg} $S$ + OLS\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25 (0) \\
 &  & $BIC_+$ &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25 (0) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9 (0) \\
 &  & $BIC_+$ & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25 (0) \\
 &  & $BIC_+$ &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25 (0) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9 (0) \\
 &  & $BIC_+$ &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ &  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25 (0) \\
 &  & $BIC_+$ &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25 (0) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9 (0) \\
 &  & $BIC_+$ & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_r}$. Sometimes $\hat{S}$ gives better results than $S$ because $S$ is penalized by the fact that it relies only on covariates not in the true model. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&  $P(S)$ &indicator &LAR  &    \textsc{CorReg} $\hat S$ + LAR& \textsc{CorReg} $S$ + LAR\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  & $BIC_+$ &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & $BIC_+$ & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  & $BIC_+$ &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  & $BIC_+$ &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ & MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  & $BIC_+$ &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  & $BIC_+$ &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_r}$. }\label{YX2linLASSO}
\end{table}

>>>>

\begin{document}
\begin{center}
{\Large
	{\sc Model-based variable selection in regression \\ with highly correlated variables.}
}
\bigskip

@@

{\bf Abstract.} Linear regression outcomes are known to be damaged by highly correlated covariates. However many modern datasets are expected to convey more and more highly correlated covariates due to the global increase of the amount of variables in datasets. We propose to explicitly model the correlations by a family of linear regressions between the covariates, some covariates explaining others. It allows then to obtain by marginalisation on the explained covariates a parsimonious correlation-free regression model. 
It corresponds to a kind of variable selection preliminary step which has then to be followed by standard linear estimation methods including classical variables selection procedures for instance. The structure of correlations is found with an MCMC algorithm aiming at optimizing a specific BIC criterion.
 An R package (\textsc{CorReg}) available on the CRAN implements this new method which will be illustrated on both simulated datasets and real-life datasets from steel industry where correlated variables are frequent.
\smallskip

@@

	With the rise of informatics, datasets contain more and more covariates, % and thus dimension reduction becomes a necessity. Moreover, 
	increasing the chance to have correlated ones.  
	 In such a context, variance of the estimators can lead to arbitrary results leading to misleading interpretations whereas interpretation and prediction are both strongly needed, depending on the context. For instance, interpretation could be favoured to improve a situation instead of only predict problems, so robust estimation is a real stake.
		~\\	~\\

%bibliographie	
	The Ordinary Least Squares (\textsc{OLS}) estimator is the minimum-variance linear unbiased estimator but it suffers from ill-conditioned matrices inversion when the covariates are highly correlated (section \ref{sectionOLS}). Some other methods try to improve the robustess of the estimator by introducing some bias, selecting only some covariates, grouping some covariates, {\it etc.}
	but many of these methods are not directly guided by the correlations whereas knowing the correlations between the covariates facilitates interpretation.

@@

	 Penalized methods try to reduce the variance introducing some bias to improve the bias-variance tradeoff and get better prediction.
	Ridge regression \cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty but
	it is the same for each covariate no matter how much it is correlated or not to others.%and will be too large for independent covariates and/or too small for correlated ones.  
	Moreover, coefficients tend to 0 but don't reach 0 so it gives difficult interpretations for large number of covariates. The absence of variable selection is not compatible with the need to find small set of relevant covariates to explain the response variable.

@@

	But it requires to suppose having many covariates with the same level of effect on the response variable and seems to stay less efficient in prediction than elastic net.
	 Spike and Slab variable selection \cite{ishwaran2005spike} also relies on Gaussian mixture (the spike and the slab) hypothesis for the regression coefficients and gives a subset of covariates (not grouped) on which to compute \textsc{OLS} but has no specific protection against correlations issues.
	We see that none of the above methods takes explicitly the correlations into account, even if the clustering methods may group the correlated covariates together.

	~\\	~\\
% Principe de la méthode
In the field of clustering, model-based explicit correlations by linear sub-regressions between covariates claims to obtain good results in both interpretation and estimation quality (like Selvarclust \cite{maugis2009variable}). But this is made in a clustering context only, with only irrelevant covariates being dependent from relevant ones (no sub-regressions between relevant or between irrelevant covariates) and the algorithm used to find the structure is a stepwise-like algorithm without protection against correlations \cite{raftery2006variable} even it is known to be often unstable \cite{miller2002subset}. We propose to transpose this method for linear regression with a specifically adapted algorithm to find the structure of sub-regression.

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&$P(S)$ &indicator &OLS  &    \textsc{CorReg} $\hat S$ + OLS& \textsc{CorReg} $S$ + OLS\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25 (0) \\
 &  & $BIC_+$ &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25 (0) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9 (0) \\
 &  & $BIC_+$ & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25 (0) \\
 &  & $BIC_+$ &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25 (0) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9 (0) \\
 &  & $BIC_+$ &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ &  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25 (0) \\
 &  & $BIC_+$ &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25 (0) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9 (0) \\
 &  & $BIC_+$ & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}_r$. Sometimes $\hat{S}$ gives better results than $S$ because $S$ is penalized by the fact that it relies only on covariates not in the true model. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&  $P(S)$ &indicator &LAR  &    \textsc{CorReg} $\hat S$ + LAR& \textsc{CorReg} $S$ + LAR\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  & $BIC_+$ &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & $BIC_+$ & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  & $BIC_+$ &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  & $BIC_+$ &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ & MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  & $BIC_+$ &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  & $BIC_+$ &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}_r$. }\label{YX2linLASSO}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&  $P(S)$ &indicator & Elasticnet  &    \textsc{CorReg} $\hat S$ + Elasticnet& \textsc{CorReg} $S$ + Elasticnet\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 499.32 (218.8) & 311.41 (137.4) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.75 (4.8) & 11.49 (4.7) \\
 &  & $BIC_+$ &MSE (sd) & 499.32 (218.8) & 307.6 (128.7) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.63 (4.7) & 11.49 (4.7) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 691.55 (503.2) & 193.45 (54.2) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 10.26 (2.7) & 7.81 (1.4) \\
 &  & $BIC_+$ & MSE (sd) & 691.55 (503.2) & 279.21 (117.3) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 13 (4.3) & 7.81 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 282.05 (134.8) & 180.64 (47.6) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 13.68 (4) & 14.05 (4) \\
 &  & $BIC_+$ &MSE (sd) & 282.05 (134.8) & 180.84 (47.5) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 14.03 (4) & 14.05 (4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 308.13 (142.9) & 129.39 (19.6) & 122.71 (17.8) \\
& & & cpl (sd) & 22.94 (7.7) & 9.37 (2.1) & 7.91 (1.4) \\
 &  & $BIC_+$ &MSE (sd) & 308.13 (142.9) & 159.14 (30.4) & 122.71 (17.8) \\
& & &cpl (sd) & 22.94 (7.7) & 15.42 (4) & 7.91 (1.4) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ & MSE (sd) & 150.14 (19.7) & 127.48 (14) & 128.21 (15) \\
& & &  cpl (sd) & 25.6 (5.4) & 14.73 (3.8) & 14.73 (3.9) \\
 &  & $BIC_+$ &  MSE (sd) & 150.14 (19.7) & 128.21 (14.9) & 128.21 (15) \\
& & & cpl (sd) & 25.6 (5.4) & 14.7 (3.9) & 14.73 (3.9) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ & MSE (sd) & 157.18 (23.5) & 110.24 (8) & 109.24 (7.8) \\
& & &  cpl (sd) & 30.41 (6.7) & 8.96 (1.3) & 8.3 (1) \\
 &  & $BIC_+$ &  MSE (sd) & 157.18 (23.5) & 123.8 (12.5) & 109.24 (7.8) \\
& & & cpl (sd) & 30.41 (6.7) & 17.18 (3.3) & 8.3 (1) \\
\hline
\end{tabular} 
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}_r$.}\label{YX2linenet}
\end{table}
